A Sample JFE Paper\footnotetext{Financial support from \ldots}

### 2018-03-14 Paper/Paper.tex

In order to confirm the results from the maximum likelihood estimation, a second estimation routine was created using the Generalized Method of Moments. The adopted strategy was to estimate $\hat{\theta}_{GMM} = (\tau + \lambda_{int,abr}, \lambda_{inc,0}, \alpha)$ by solving equation~\eqref{eq:GMM} with the actual and the estimated moments ($m^d(x)$ and $m^e(x|\theta_{GMM})$, respectively, where $x$ is the real data).

@@

\section{Results}\label{sec:Results}

>>>>

\subsection{Link Between Patent Citations and Theory}
Multiple assumptions are needed to relate the various features of the patent citation dataset to our theoretical model:
\begin{itemize}
	\item Every patent represents a single innovation.
	\item Abrupt patents will receive more total citations than incremental patents.
	\item An abrupt patent receives a citation from a patent within its same classification if and only if the citing patent represents an incremental innovation within the abrupt patent’s technology cluster.
	\item Internal innovations will receive more self-citations (citations from future patents by that same company) than external innovations.
\end{itemize}
Assumptions one, two, and four are made in AK2016 based on empirical evidence (albeit of varying degrees). Assumption three is very important to our estimation scheme. It states that every incremental innovation will cite the abrupt patent that started its technology cluster, and that they will always be within the same patent classification. The provides a clear link between the data and the theoretical distribution in equations 14-15. If an abrupt innovation’s technology cluster had k incremental innovations, that abrupt innovation’s patent will receive k same-class citations.

Of course, to estimate the model we also need to identify the abrupt patents. Assumption two tells us that the abrupt patents will have more total citations (same-class plus external-class citations), but it does not give us an exact cutoff. In AK2016 they estimate that the upper ten percent of the total citation distribution contains the abrupt patents, so we use this cutoff in our baseline estimation. Later we test the robustness of our estimates to changes in this value.

Using the ten-percent cutoff, we can generate the distribution of same-class citations to abrupt patents (see figure 4). This empirical distribution will be fit to our theoretical distribution from equations 14-15 to estimate the model. Two important features of the empirical distribution is the large mass of patents at zero citations and the large upper tail.

It should be noted that, even if the four assumptions listed above are completely accurate, we would expect some abrupt patents to be wrongly classified as incremental due to our ten percent cutoff. According to our theoretical model, there is a chance that an abrupt innovation’s technology cluster will be replace very early on by another abrupt innovation, meaning that it will receive very few same-class citations. While the abrupt patent could still receive out of class citations after being replaced (and in fact, we do see many patents with zero same-class citations but many external citations), it could not receive enough to be classified as abrupt. Thus, we expect the empirical distribution in figure 4 to underestimate the amount of abrupt patents with low numbers of citations. The impact of this potential bias on our estimation is discussed below.

\subsection{MLE Estimation}

According to equations 14-15, the theoretical citation distribution of abrupt patents only depends on three parameters: $\alpha$, $\lambda_{inc,0}$, and $\lambda_{abr, int} + \tau$. In addition, the distribution is identical at equal ratios of the arrival rate parameters, so it actually only depends on two independent parameters: $\alpha$ and $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$. Intuitively, $\alpha$ governs rate at which the incremental innovation step size decays after multiple incremental innovations ($\alpha$ equal to one implies a constant step size). The value of  $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$ is determined by the relative amount of incremental compared with abrupt innovations in the entire economy.

Given a set of parameter values, the resulting citation distribution looks like a gamma distribution, with a large upper tail and the possibility of a mode greater than zero. A larger value of $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$  means that there are relatively more abrupt innovations, which means that more product lines will be replaced before their originating patents can accrue a large number of citations. Thus, increasing $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$ shifts the distribution to the left. Reducing the value of $\alpha$ means that the firms will invest relatively more in incremental innovation early in the product lifecycle (due to the diminishing returns to incremental innovation). For low enough values of $\alpha$, this can lead to a peak in the distribution at a citation value greater than zero, as firms almost always invest in the first incremental innovation but invest increasingly less in the late ones. Theoretical graphs for various parameter values are shown in figure 5.

We estimate the two parameters using maximum likelihood estimation. Our theoretical model gives a probability mass distribution for every whole number of citations, but the actual data shows fractional values (this is because, to address the fact that newer patents did not have as long of a time to gain citations, we used a measure of expected citations that allowed for non-whole numbers). To address this, we rounded the expected citation variable to the nearest whole number, and then took the likelihood as the theoretical pmf value at that point.

The resulting parameter estimates are shown in figure 6, and the fit is plotted in figure 7.  The estimated ratio of incremental to abrupt patents is about 10:1, which is consistent with the fact that we defined the upper ten percent of patents in the citation distribution as being abrupt. The estimate of $\alpha$ is equal to one. This indicates that firms do not face diminishing returns to initial investment. This has very important theoretical implications, which will be discussed later on.

Looking at figure 7, we see that the data fits most of the distribution closely (including the upper tail, which is not pictured), but significantly underestimates the amount of zero-citation patents. We find that, when observations in the upper tail are eliminated, the estimation better fits the zero-citation data (see figure 8), indicating that the model is unable to completely capture both of those features. Now, it may seem fairly ad-hoc to eliminate observations in the upper tail, but there may be a theoretical justification for doing so. Our model, in keeping with AK2016, only allows for two scales of innovation: abrupt and incremental. This assumption seems to be made only for mathematical simplicity; while there is plenty of evidence that some patents are more valuable than others, there seems to be no evidence of a binary distinction. One might expect that patents in the upper tail of our empirical distribution (it had a max of 741 citations) are significantly more productive than the others. However, under our simple binary model, those patents are identical to the others from a productivity standpoint, and the only reason they gained more citations was through chance. Thus, because a more complete model may place the upper-tail observations in a separate classification, it is reasonable to be suspicious of estimation results that are pinned down by the upper tail.

Multiple methods were used to make sure that the parameter values given in figure 6 were in fact those that maximize the log-likelihood function. First, many initial values were used in the optimization algorithm, and it always gave the same result. We also tried fixing the value of $\alpha$ and running an unconstrained optimization to determine $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$, and this also gave the same result (the motivation being that the unconstrained algorithm is sometimes less sensitive to initial conditions). Finally, the 3d plot of the negative log-likelihood clearly shows a minimum at our parameter values (see figure 8), and a basin hopping algorithm found no other minimum.

Recall that our empirical distribution likely underestimates the number of abrupt patents with a low number of citations. This implies that our theoretical model may actually be even worse at fitting the zero-citation density than figure 7 would suggest. It also implies that our estimate of $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$ may be biased downward. Importantly, however, because lowering $\alpha$ leads to a decrease in the theoretical density at zero, this downward bias is probably not impacting our estimate of $\alpha$; if the bias was corrected, we would still expect $\alpha$ to be equal to one.

\subsection{First Robustness Check: GMM Estimation}

Before drawing strong conclusions from our estimation, we ran several robustness checks. These were meant to test the sensitivity of our estimates both to changes in the estimation procedure and to changes in theoretical assumptions.  We are mainly interested in seeing if $\alpha$ remains equal to one (no diminishing returns to incremental innovations) and if the model's fit to the data is affected.

First, we re-estimated the parameters using an alternative estimation scheme: Generalized Method of Moments. The adopted strategy was to estimate $\hat{\theta}_{GMM} = (\tau + \lambda_{int,abr}, \lambda_{inc,0}, \alpha)$ by solving equation~\eqref{eq:GMM} with the actual and the estimated moments ($m^d(x)$ and $m^e(x|\theta_{GMM})$, respectively, where $x$ is the real data).

@@

\subsection{Other Robustness Checks}

The GMM results suggest that the main features of our MLE estimation are not simply artifacts of that specific estimation strategy. Given our theoretical model, the best fit of the data truly seems to be one where the density at zero is underestimated and where alpha is equal to one.

As far as theoretical assumptions, one of our most arbitrary is the assumption that abrupt patents are those in the upper ten percent of the total citation distribution. While the ten percent value is similar to the one estimated by AK2016, and is used in other papers, those papers use a different theoretical model. Furthermore, there is no defining feature of the citation distribution at the ten percent cutoff (no discontinuity or anything). Considering this, it is necessary to check whether our results are robust to changes in this cutoff.

The MLE estimates for cutoffs of 20\% and 5\%, alongside the baseline results, are shown in figure 9. We see that the arrival rates move in the direction that you would expect; the relative amount of abrupt patents drops when the cutoff is 5\% and increases when the cutoff is 20\%. More importantly, we find that $\alpha$ is still equal to one.

Next we focused on the assumption that an incremental patent will always cite the abrupt patent that initiated its technology cluster. This assumption, which we initially made for mathematical simplicity, is inconsistent with the conclusions of AK2016. In their model, they included a certain probability $p$ that an abrupt patent will be cited by subsequent incremental patents, which was estimated to be 75\%. Adding this parameter to our model is simple. For a technology cluster of size $k$, the probability of the abrupt patent having $i$ citations is given by the binomial distribution:
\begin{equation} \label{eq:prob}
Prob_{i, k} = Binom{i, k, p}
\end{equation}
Thus, given the size distribution $\eta_k$ from equations 14-15, the citation distribution $f_i$ is given by:
\begin{equation} \label{eq:cit_dist}
f_i = \displaystyle\sum_{k=0}^{\infty}\eta_k * Prob_{i, k}
\end{equation}
The addition of the probability parameter $p$ gives the model more flexibility. A lower value of $p$ shifts the distribution left.

The MLE estimates for this updated model are presented in table 10 and figure 11. We see that $p$ is equal to one, with the other parameters identical to our baseline model. This seems to validate our original assumption of setting $p$ equal to one. There are a few caveats, however, with this robustness check. First, as was mentioned above, even in our baseline model there is a problem with the classification of abrupt patents. It is likely that abrupt patents which are displaced early on by another abrupt patent will never gain enough citations to reach our cutoff value. This leads our empirical distribution (shown in figure 2) to underestimate the number of abrupt patents with a low number of citations. When the probability of citing is less than one, we would expect this underestimation to be even greater. This bias could cause us to overestimate the value of $p$.

While we were able to test the robustness of our estimation to multiple key theoretical assumptions, there are still others that have not been checked. Of these, we think the most in need of support are assumptions 1-2 from the citation section: that abrupt patents will receive a large number of total citations and that same-class citations are those that directly fall within the abrupt patent’s technology cluster. Intuitively, this seems like it may be a good approximation, and it is similar to other assumptions made in previous Akcigit papers, but we do not have any actual empirical evidence to support it. Considering that our whole estimation strategy rests on those assumptions, further empirical research into their validity is needed.

\section{Results}\label{sec:Results}
%Add a further discussion of the importance of alpha =1 in relation to the broader motivations of the paper (that is, its relations to intertemporal tfp choice).

Through all robustness checks, the most constant result was that $\alpha = 1$. This has very important theoretical implications.
